
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

How many physical points must be referenced when speaking of the following electrical quantities?

\vskip 10pt

\item{$\bullet$} Voltage
\item{$\bullet$} Current
\item{$\bullet$} Resistance

\vskip 10pt

In other words, does it make sense to speak of voltage at a single point, or between two points, or between three points, etc.?  Does it make sense to speak of current at a single point, between two points, between three points, etc.?

\underbar{file 00147}
%(END_QUESTION)





%(BEGIN_ANSWER)

\item{$\bullet$} Voltage is always measured {\it between two points}.
\item{$\bullet$} Current may be measured at a single point (at a cross-section of a conductive path).
\item{$\bullet$} Resistance is always measured {\it between two points}.

\vskip 10pt

Follow-up question: explain, if you can, the relevance of these facts to electrical safety.  For example, why is it important to know that voltage is always a quantity existing {\it between} two points (rather than existing {\it at} a single point) when considering your personal safety?

%(END_ANSWER)





%(BEGIN_NOTES)

One of the more confusing aspects of electrical theory is that both voltage and resistance are quantities relative between two points.  It is meaningless to speak of the amount of voltage "at this point" in a circuit, at least without implying a reference point such as ground.  The same goes for resistance: it makes no sense to speak of how much electrical resistance there is "at this point" in a circuit either.

Conversely, it makes perfect sense to speak of either voltage or resistance lying "between {\it this} point and {\it that} point," because both these quantities are relative between exactly two points.

Current, on the other hand, is the coordinated motion of electric charge through a conductor.  As such, it may be measured at any single point in a circuit, like measuring the flow of water in a river at any one particular cross-sectional sample.

%INDEX% Voltage, measuring
%INDEX% Current, measuring
%INDEX% Resistance, measuring

%(END_NOTES)


