
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Suppose that an electromechanical relay has a coil voltage rating of 5 volts, and a coil resistance of 250 $\Omega$.  However, you desire to energize this relay with a 24 volt power supply.  You know that a series-connected resistor might enable the 5-volt relay coil to be powered by the 24-volt supply without damage, but you do not know what size of resistor would be appropriate for the task.

Draw a schematic diagram for such a circuit, showing the power supply (battery symbol), relay, and resistor.  Explain how the resistor's value would be calculated, along with the calculated value in ohms.

\underbar{file 00289}
%(END_QUESTION)





%(BEGIN_ANSWER)

Resistor value = 950 $\Omega$.

%(END_ANSWER)





%(BEGIN_NOTES)

Do not be surprised if many of your students neglect to calculate the resistor's necessary {\it power} dissipation rating for the resistor, simply because this value was not requested in the question.  However, it is important for students to be actively thinking about every problem they encounter, and to try to take all relevant factors into consideration!  

In real life, the power dissipation rating of such a resistor would be {\it very} important.  Failing to account for this value could result in component (and system) failure.

%INDEX% Ohm's Law, quantitative

%(END_NOTES)


