
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Suppose the foot-ground contact resistance of a person standing barefoot is 3 k$\Omega$, the contact resistance between a person's hand and a held wire is 10 k$\Omega$, and the person's hand-to-foot internal body resistance is 500 $\Omega$.  How much danger would a person be in, given these conditions, if the voltage between the wire they were holding and the ground they were standing on was 120 volts, 60 Hz alternating current?

\underbar{file 00305}
%(END_QUESTION)





%(BEGIN_ANSWER)

According to research done by Charles F. Dalziel, the amount of current that would go through this individual would be sufficient to cause pain, but not enough to cause loss of voluntary muscle control.

%(END_ANSWER)





%(BEGIN_NOTES)

This question is not only a practical exercise of Ohm's Law, but also a stimulus for researching shock current levels and their effects on the human body.  Be sure pursue a line of questioning here during discussion time to explore the effects of electric current on the human body for a wide range of currents.  In other words, don't just leave the answer at "causes pain, but muscle control maintained," but rather use this time to investigate what levels of current cause more (and less) serious effects on the human body.

Also, be sure to point out that the health of the individual being shocked is important to consider.  Dalziel's work was based on healthy individuals, who had been medically screened for this testing.  A person in ill health may not fare as well in the same scenario.

%INDEX% Electric shock

%(END_NOTES)


