
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

What is a {\it megger}, and what type of resistance measurements would it typically be used for?  Explain how the design of a "megger" differs from that of a normal ohmmeter.

Also, explain how improper use of a "megger" may actually be hazardous, either to the operator of the meter or to the circuit under test.

\underbar{file 00311}
%(END_QUESTION)





%(BEGIN_ANSWER)

A "megger" is a high-range ohmmeter, typically used to measure the resistance of wire insulation.  They utilize relatively high voltage (upwards of 1000 VDC) to measure resistance.

\vskip 10pt

Follow-up question: what is a {\it hi-pot} meter, and what function is it typically used for?

\vskip 10pt

Challenge question: why are special, high-voltage ohmmeters even needed?  What's wrong with using a regular ohmmeter that outputs just a few volts to measure resistance?  What does the existence of these specialized ohmmeter types tell us about the nature of electrical resistance?

%(END_ANSWER)





%(BEGIN_NOTES)

"Meggers" are very useful tools, but they can cause damage as well.  Your students need to be aware of proper and improper uses of "meggers" before they are entrusted with the use of one.

The challenge question is worth exploring if time permits!  In real life, the simplicity of Ohm's Law is deceptive . . .

%INDEX% Megger, defined
%INDEX% Safety, electrical

%(END_NOTES)


