
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

What is the significance of a transistor's {\it beta} ($\beta$) rating?  What, exactly, does this figure mean?  Explain how you might set up an experiment to calculate the beta of a given transistor.

\vskip 5pt

Obtain a copy of a {\it datasheet} for a small-signal transistor such as the {\tt 2N2222} and see what it has to say about that transistor's beta.  Note: the beta of a transistor may be represented by the Greek letter ($\beta$), or by a completely different symbolism known as a {\it hybrid parameter}: $h_{FE}$

\underbar{file 00482}
%(END_QUESTION)





%(BEGIN_ANSWER)

$\beta_{DC} = {I_C \over I_B}$

\vskip 10pt

$\beta_{AC} = {\Delta I_C \over \Delta I_B}$

%(END_ANSWER)





%(BEGIN_NOTES)

The "beta" rating of a transistor is a very important, yet very elusive parameter.  Discuss the meaning of this specification with your students, and also their experimental setups for empirically determining beta.  Then, compare the results of this discussion with the figures obtained from their datasheets.  What do the datasheet figures indicate about the nature of beta as a parameter?

After sharing the datasheet results, re-discuss the experimental setups for measuring beta.  Would a single test be sufficient, or would it be advisable to test beta more than once for a given transistor?

%INDEX% Beta, defined for a BJT

%(END_NOTES)


