
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Based on these DC continuity tester indications, what type of transistor is this, PNP or NPN?

\medskip
\item{$\bullet$} Resistance with negative test lead on pin 1, positive test lead on pin 2: {\it no continuity}
\item{$\bullet$} Resistance with negative test lead on pin 1, positive test lead on pin 3: {\it no continuity}
\item{$\bullet$} Resistance with negative test lead on pin 2, positive test lead on pin 1: {\it no continuity}
\item{$\bullet$} Resistance with negative test lead on pin 2, positive test lead on pin 3: {\it no continuity}
\item{$\bullet$} Resistance with negative test lead on pin 3, positive test lead on pin 1: {\bf continuity}
\item{$\bullet$} Resistance with negative test lead on pin 3, positive test lead on pin 2: {\bf continuity}
\medskip

Also, to the best of your ability, identify the transistor's three terminals (emitter, base, and collector).

\underbar{file 00483}
%(END_QUESTION)





%(BEGIN_ANSWER)

This is a PNP transistor.  Pin 3 is the base, and pins 1 and 2 are emitter/collector or collector/emitter (can't be sure which).

%(END_ANSWER)





%(BEGIN_NOTES)

Advise your students about the risks of using an analog multimeter (in ohmmeter mode) to test semiconductor components.  Some inexpensive analog multimeter designs actually {\it switch} the polarity of the test leads when in the ohmmeter mode.  In other words, the red test lead actually connects to the negative side of the meter's internal battery, while the black test lead connects to the positive side of the internal battery!  If you are used to associating red with positive and black with negative, this switch will be quite a surprise.

Ask your students: what effect would a switch in polarity such as the one just described have on the determination of a transistor's identity?  What if the person thought their meter's red lead was positive and the black lead negative, when in fact it was just the opposite?  Would this affect their ability to accurately identify the transistor's terminals?  Why or why not?

%INDEX% BJT, terminal identification

%(END_NOTES)


