
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

In very simple, qualitative terms, rate the impedance of capacitors and inductors as "seen" by low-frequency and high-frequency signals alike:

\medskip
\item{$\bullet$} Capacitor as it "appears" to a low frequency signal: (\underbar{high} or \underbar{low}) impedance?
\item{$\bullet$} Capacitor as it "appears" to a high frequency signal: (\underbar{high} or \underbar{low}) impedance?
\vskip 10pt
\item{$\bullet$} Inductor as it "appears" to a low frequency signal: (\underbar{high} or \underbar{low}) impedance?
\item{$\bullet$} Inductor as it "appears" to a high frequency signal: (\underbar{high} or \underbar{low}) impedance?
\medskip

\underbar{file 00616}
%(END_QUESTION)





%(BEGIN_ANSWER)

\medskip
\item{$\bullet$} Capacitor as it "appears" to a low frequency signal: {\it high} impedance.
\item{$\bullet$} Capacitor as it "appears" to a high frequency signal: {\it low} impedance.
\vskip 10pt
\item{$\bullet$} Inductor as it "appears" to a low frequency signal: {\it low} impedance.
\item{$\bullet$} Inductor as it "appears" to a high frequency signal: {\it high} impedance.
\medskip

\vskip 10pt

Challenge question: what does a capacitor "appear" as to a {\it DC} signal?

%(END_ANSWER)





%(BEGIN_NOTES)

Ask your students how they arrived at their answers for these qualitative assessments.  If they found difficulty understanding the relationship of frequency to impedance for reactive components, I suggest you work through the reactance equations qualitatively with them.  In other words, evaluate each of the reactance formulae ($X_L = 2 \pi f L$ and $X_C = {1 \over {2 \pi f C}}$) in terms of $f$ increasing and decreasing, to understand how each of these components reacts to low- and high-frequency signals.

%INDEX% Capacitors versus inductors, impedances at low and high frequencies
%INDEX% Impedance, of capacitor
%INDEX% Impedance, of inductor
%INDEX% Inductors versus capacitors, impedances at low and high frequencies

%(END_NOTES)


