
%(BEGIN_QUESTION)
% Copyright 2008, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Transistor operation may be explained in terms of three different currents: {\it injection}, {\it diffusion}, and {\it collection}.  Describe what each of these currents are, and how they help explain the amplifying nature of a transistor.

\underbar{file 00915}
%(END_QUESTION)





%(BEGIN_ANSWER)

"Injection" current consists of those majority charge carriers (either electrons or holes, depending on the transistor type) that are "injected" from the emitter region into the base region of a transistor.  "Diffusion" current is the current through the base terminal of the transistor resulting from recombination of electrons and holes in the emitter-base junction.  Most of the injection current, however, becomes "collection" current and goes through the collector terminal of the transistor.

%(END_ANSWER)





%(BEGIN_NOTES)

As students research and use these terms in their study of bipolar junction transistors, the theory of BJT operation should become more evident.  The terms really are well-chosen, accurately representing the motions of charge carriers within the transistor structure.

The base is doped much lighter than the emitter so that the collection current will greatly exceed the diffusion current.  If the two layers were equally doped, the base-emitter junction would tend to act as a normal diode, passing nearly all the injection current through the base terminal.  As it is, only a small portion of the injected charge carriers diffuse into the base, the rest being ``collected'' by the collector layer.

The collector is not as heavily doped as the emitter, in order that the collector-base junction will have a greater reverse breakdown voltage.  Since this junction typically operates in reverse-bias mode with a substantial voltage drop, the breakdown voltage rating is important.

%INDEX% Collection current, BJT
%INDEX% Diffusion current, BJT
%INDEX% Injection current, BJT

%(END_NOTES)


