
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Not all "zener" diodes break down in the exact same manner.  Some operate on the principle of {\it zener breakdown}, while others operate on the principle of {\it avalanche breakdown}.  How do the temperature coefficients of these two zener diode types compare, and how are you able to discern whether a zener diode uses one principle or the other just from its breakdown voltage rating?

Correspondingly, is there a way we could determine the type of breakdown action from experimental measurements on a zener diode?  Explain how such an experiment might be set up.

\underbar{file 01053}
%(END_QUESTION)





%(BEGIN_ANSWER)

Low-voltage zener diodes have negative temperature coefficients, because they exploit the {\it zener effect}.  High-voltage zener diodes have positive temperature coefficients, because they exploit the {\it avalanche effect}.  I'll let you research how to tell the difference between zener diodes employing each phenomenon on your own!

\vskip 10pt

Challenge question: explain the difference between the "zener" and "avalanche" effects, in terms of charge carrier action.

%(END_ANSWER)





%(BEGIN_NOTES)

Regular "rectifying" diodes also have temperature coefficients.  Ask your students to identify whether the temperature coefficient for a rectifying diode is typically positive or negative, and what this actually means.  It is very easy to experimentally verify this, so you may want to ask your students to demonstrate how to determine the sign of a rectifying diode's temperature coefficient as a prelude to reviewing the experimental portion of the original question.

Ask your students to identify the typical voltage values associated with both types of breakdown effect.  This will quickly reveal which students did their research for this question, as opposed to those who merely read the answer given here!

%INDEX% Breakdown, zener versus avalanche
%INDEX% Zener diode, behavior

%(END_NOTES)


