
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Suppose a friend of yours recently purchased an off-road vehicle.  This friend also purchased a military-surplus spotlight, which he thinks would be a great accessory for off-road illumination at night.  The only problem is, the spotlight is rated for 24 volts, while the electrical system in his vehicle is 12 volt.

Your friend asks you to engineer a solution for powering the 24-volt spotlight with the 12 volts available on his vehicle.  Of course, you are not allowed to modify the vehicle's electrical system (change it to 24 volt generator, battery, starter motor, etc.), because it is new and still under warranty.  What do you recommend to your friend?

Draw a component-level schematic diagram of your solution to this problem.

\underbar{file 01099}
%(END_QUESTION)





%(BEGIN_ANSWER)

While there are several different methods which could be used here to transform 12 volts into 24 volts, I will not reveal any of them here, lest I spoil the fun for you!

%(END_ANSWER)





%(BEGIN_NOTES)

Students may be inclined to give easy answers to this problem ("use a DC-DC converter!"), but the purpose of it is for students to explore solutions at the {\it component level}.  Even if they do not yet understand how the circuitry works, they should be able to find complete solutions in their research, or at least enough schematics for sections of the conversion process for them to engineer a complete solution.

Remind your students that this is a powerful spotlight they're going to have to power!  Their conversion system may have to handle hundreds of watts.

%INDEX% Converter circuit, automotive application

%(END_NOTES)


