
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Suppose you come across a relay that is said to have "Form C" contacts.  What does this phrase mean?  And, is there such a thing as either "Form A" or "Form B" contacts?

\underbar{file 01387}
%(END_QUESTION)





%(BEGIN_ANSWER)

"Form C" is just another way of saying "SPDT" with regard to switch or relay contacts.  

%(END_ANSWER)





%(BEGIN_NOTES)

When I first heard of a switch having "Form C" contacts, I had absolutely no idea what it meant.  I was quite familiar with "single-pole, double-throw," but not this new term.  Different industries often use different terms for describing the same things.  Your students should be made aware that there is a tendency for people to become "isolated" within their respective industries or fields of expertise, to the point where they may be unaware of alternative terms for the same things (Form-C versus SPST is a good example of this).  Your students may even find themselves misjudged by others for not knowing the peculiar and specialized terms used within certain industries, when they first obtain employment.  In many ways it is akin to the misunderstandings arising when different cultures meet: people have the general tendency to think their way of doing things is the {\it only} way.  Bridging such cultural divides requires patience, humility, and tact.

%INDEX% Contacts, form A
%INDEX% Contacts, form B
%INDEX% Contacts, form C

%(END_NOTES)


