
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

It may seem difficult to even start on a project such as this, with no schematic diagram provided.  Identify a few different sources of information where you might find sample voltage regulator circuits, to begin your design from.

Why do you suppose your instructor decided to challenge you with a project such as this, with no schematic diagram to follow and plenty of things to potentially go wrong?

\underbar{file 01520}
%(END_QUESTION)





%(BEGIN_ANSWER)

I'll let you determine where sample voltage regulator circuit designs may be found.

\vskip 10pt

As to the question of why the instructor would challenge you in this way, the answer is quite simple: to prepare you for the realities of a challenging career in electronics.  Think of this project as being a small-scale example of the work world, where you will be required to overcome technical obstacles on a routine basis, often with little or no assistance.

Challenges are a fact of life.  It would be unrealistic to expect you to have immediate answers to every challenge you will ever face.  What {\it is} expected of you, however, is a positive attitude and the skillful persistence to {\it find} those answers in due time.

%(END_ANSWER)





%(BEGIN_NOTES)

Not much needs to be said here!

%(END_NOTES)


