
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

A friend of yours brings you their damaged stereo amplifier, hoping that perhaps you would be able to repair it cheaper than the local electronics repair shop.  The amplifier was damaged at a recent party, when one of your friend's guests turned up the volume to full and left it there until smoke billowed out of the power amplifier chassis.

Your friend has already done some troubleshooting of his own: after turning off the amplifier and letting the smoke clear, he turned it back on at low volume to find that the left channel is dead, but the right channel is still working.  He then swapped speakers and speaker wires, and consistently found that whatever speaker was plugged into the left channel did not make sound, but the speaker plugged into the right channel always did.

You remove the chassis cover on the amplifier and look inside.  There, the damage is visually apparent: both of the power transistors for the left channel output are burnt beyond recognition.  You unsolder the transistors from the circuit board and unscrew them from the heat sink, but you cannot read the part numbers on their cases due to the thermal damage.  This is not good, because without knowing the proper part numbers, your friend cannot order the proper replacement transistors to repair the amplifier.

As usual, there is no schematic diagram supplied with this amplifier that would indicate the proper part numbers.  What do you do?

\underbar{file 01589}
%(END_QUESTION)





%(BEGIN_ANSWER)

Read the part numbers off the power transistors for the right channel output!

%(END_ANSWER)





%(BEGIN_NOTES)

Some students may question this logic, believing that the left and right channels of a stereo amplifier would be mirror-symmetric rather than identical, and thus possibly contain different components.  You may answer this objection by appealing to the indistinguishable sound of the two channels, when listened to separately (mono).  There is nothing "right-handed" or "left-handed" about the two channels.  Each one is identical to the other at the circuit level, because each channel is expected to perform exactly the same.

%INDEX% Troubleshooting, stereo power amplifier example
%INDEX% Troubleshooting, making note of interchangeable components

%(END_NOTES)


