
%(BEGIN_QUESTION)
% Copyright 2005, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Briefly answer the following safety questions:

\medskip
\item{$\bullet$} What does electric current do to muscle tissue?
\item{$\bullet$} What can electric current do to motor muscles (fingers, arms, legs)?
\item{$\bullet$} What can electric current do to heart and lungs?
\item{$\bullet$} Why should you use one hand while working on live power circuits?  Which hand?
\item{$\bullet$} Why is water dangerous when working around electric power?
\item{$\bullet$} Why is metal jewelry dangerous to wear when working on electric circuits?
\item{$\bullet$} What kinds of tools are best for working on live power circuits?
\item{$\bullet$} What kind of immediate medical attention does an electric shock victim require?
\item{$\bullet$} What footwear is appropriate when working around electric power?
\item{$\bullet$} What footwear is {\bf not} appropriate when working around electric power?
\medskip

\underbar{file 01702}
%(END_QUESTION)





%(BEGIN_ANSWER)

\medskip
\item{$\bullet$} What does electric current do to muscle tissue?  {\it Electric current causes muscles to contract.}
\item{$\bullet$} What can electric current do to motor muscles (fingers, arms, legs)?  {\it It may cause them to involuntarily contract.}
\item{$\bullet$} What can electric current do to heart and lungs?  {\it Paralyze them.}
\item{$\bullet$} Why should you use one hand while working on live power circuits?  {\it To minimize the danger of an across-the-chest path for electric current.}  Which hand?  {\it The right, because the heart is more vulnerable to shock current going through the left-hand side of the chest.}
\item{$\bullet$} Why is water dangerous when working around electric power?  {\it It lowers the resistance of porous substances, including human skin.}
\item{$\bullet$} Why is metal jewelry dangerous to wear when working on electric circuits?  {\it Because the metal pieces optimize contact between your skin and an exposed power conductor, or between two power conductors.}
\item{$\bullet$} What kinds of tools are best for working on live power circuits?  {\it Tools with electrically-insulated handles.}
\item{$\bullet$} What kind of immediate medical attention does an electric shock victim require?  {\it CPR if they are not breathing or their heart is not beating.}
\item{$\bullet$} What footwear is appropriate when working around electric power?  {\it Closed-toed work boots or shoes with good, thick, insulating soles.}
\item{$\bullet$} What footwear is {\bf not} appropriate when working around electric power?  {\it Sandals, flip-flops, or other shoes exposing the skin.}
\medskip

%(END_ANSWER)





%(BEGIN_NOTES)

The safety concern of jewelry worn around electric circuits is not limited to high voltages where shock is possible.  It is also a concern around low-voltage circuits where high current through a ring or bracelet (caused by bridging two conductors with the jewelry) can cause the jewelry to heat up and burn the skin.

%INDEX% Safety, list of "common-sense" questions

%(END_NOTES)


