
%(BEGIN_QUESTION)
% Copyright 2003, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

The "beta" ratio ($\beta$) of a bipolar junction transistor, sometimes alternatively referred to as $h_{FE}$, is a very important device parameter.  In essence, it describes the amplifying power of the transistor.  Give a mathematical definition for this parameter, and provide some typical values from transistor datasheets.

\underbar{file 02038}
%(END_QUESTION)





%(BEGIN_ANSWER)

$\beta$ is defined as the ratio between collector and base current.  I'll let you research some typical values.  Here are some transistor part numbers you could research datasheets for:

\medskip
\goodbreak
\item{$\bullet$} {\tt 2N2222}
\item{$\bullet$} {\tt 2N2905}
\item{$\bullet$} {\tt 2N2907}
\item{$\bullet$} {\tt 2N3403}
\item{$\bullet$} {\tt 2N3703}
\item{$\bullet$} {\tt 2N3904}
\item{$\bullet$} {\tt 2N3906}
\item{$\bullet$} {\tt 2N4125}
\item{$\bullet$} {\tt 2N4403}
\item{$\bullet$} {\tt 2N3055}
\item{$\bullet$} {\tt TIP 29}
\item{$\bullet$} {\tt TIP 31}
\item{$\bullet$} {\tt TIP 32}
\item{$\bullet$} {\tt TIP 41}
\item{$\bullet$} {\tt TIP 42}
\medskip

\vskip 10pt

Follow-up question \#1: what conditions affect the $\beta$ ratio of a transistor?

\vskip 10pt

Follow-up question \#2: re-write the $\beta$ equation to solve for the other variables ($I_C = \cdots$ , $I_B = \cdots$).

%(END_ANSWER)





%(BEGIN_NOTES)

Ask your students to show you at least one datasheets for one of the listed transistors.  With internet access, datasheets are extremely easy to locate.  Your students will need to be able to locate component datasheets and application notes as part of their work responsibilities, so be sure they know how and where to access these valuable documents!

The follow-up question is an important one to discuss, as $\beta$ is far from stable for most transistors!  This point is often overlooked in basic electronics textbooks, leaving students with the false impression that transistor circuit calculations using $\beta$ are far more accurate than they actually are.

%INDEX% Beta, defined for a BJT
%INDEX% h(fe), defined for a BJT

%(END_NOTES)


