
%(BEGIN_QUESTION)
% Copyright 2005, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

Examine this truth table and then write both SOP and POS Boolean expressions describing the Output:

% No blank lines allowed between lines of an \halign structure!
% I use comments (%) instead, so that TeX doesn't choke.

$$\vbox{\offinterlineskip
\halign{\strut
\vrule \quad\hfil # \ \hfil & 
\vrule \quad\hfil # \ \hfil & 
\vrule \quad\hfil # \ \hfil & 
\vrule \quad\hfil # \ \hfil \vrule \cr
\noalign{\hrule}
%
% First row
A & B & C & Output \cr
%
\noalign{\hrule}
%
% Second row
0 & 0 & 0 & 1 \cr
%
\noalign{\hrule}
%
% Third row
0 & 0 & 1 & 0 \cr
%
\noalign{\hrule}
%
% Fourth row
0 & 1 & 0 & 1 \cr
%
\noalign{\hrule}
%
% Fifth row
0 & 1 & 1 & 0 \cr
%
\noalign{\hrule}
%
% Sixth row
1 & 0 & 0 & 0 \cr
%
\noalign{\hrule}
%
% Seventh row
1 & 0 & 1 & 1 \cr
%
\noalign{\hrule}
%
% Eighth row
1 & 1 & 0 & 1 \cr
%
\noalign{\hrule}
%
% Ninth row
1 & 1 & 1 & 0 \cr
%
\noalign{\hrule}
} % End of \halign 
}$$ % End of \vbox

Which of those Boolean expressions is simpler for this particular truth table?  Which will be easier to reduce to simplest form (for the purpose of creating a gate circuit to implement it)?

\underbar{file 02823}
%(END_QUESTION)





%(BEGIN_ANSWER)

SOP expression:

$$\overline{A} \> \overline{B} \> \overline{C} + \overline{A} B \overline{C} + A \overline{B} C + A B \overline{C}$$

POS expression:

$$(A + B + \overline{C})(A + \overline{B} + \overline{C})(\overline{A} + B + C)(\overline{A} + \overline{B} + \overline{C})$$

\vskip 10pt

Note: before deciding which expression is simpler, remember that the POS expression must be distributed before we may apply any of the standard Boolean simplification rules.

\vskip 10pt

Follow-up question: compare and contrast the procedures for generating SOP versus POS expressions from a truth table.  What states (1 or 0) are you looking for when writing each type of expression?  Explain why.

\vskip 10pt

Challenge question: what truth table scenarios do you suppose would "favor" an SOP expression over a POS expression, and visa-versa?  In other words, under what conditions does a truth table yield a simpler SOP expression, versus a simpler POS expression?

%(END_ANSWER)





%(BEGIN_NOTES)

This question is really asking students to compare and contrast SOP against POS expressions, rather than being a question specific to the given truth table.  The actual expressions given in the answer are there only for "drill," so students may check their work.  The {\it real} answers relate to the follow-up and challenge questions!

%INDEX% POS expression, Boolean algebra (from analysis of a truth table)
%INDEX% Product-of-Sums expression, Boolean algebra (from analysis of a truth table)
%INDEX% SOP expression, Boolean algebra (from analysis of a truth table)
%INDEX% Sum-of-Products expression, Boolean algebra (from analysis of a truth table)

%(END_NOTES)


