
%(BEGIN_QUESTION)
% Copyright 2005, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

When first learning about encoders, decoders, multiplexers, and demultiplexers, students often get them confused with one another.  Write succinct definitions (complete with illustrations) for each of these four digital functions, based on your own research and written using your own words.  Also, identify which two of these digital functions are usually performed by the same integrated circuit.

\vskip 300pt

\underbar{file 03179}
%(END_QUESTION)





%(BEGIN_ANSWER)

I'll let you figure out the first part of the answer (four succinct definitions, complete with illustrations)!  Because it is so easy to get these four functions mixed up in your mind, it is important that you arrive at your own understanding of which is which, rather than have someone else (like me) provide ready-made definitions for you to memorize.

\vskip 10pt

{\it Decoding} and {\it demultiplexing} are usually performed by the same integrated circuit device.  A good example of this is the 74HC154.

%(END_ANSWER)





%(BEGIN_NOTES)

Here is a good example of where students like to fall on rote memorization, and where such shallow learning strategies often fail.  It is imperative that students do their own research and cast these functions into their own personal terms.  This way, they will understand the differences rather than just memorize the differences.

Call on individual students to present their findings for this question, and let the classroom be a place where students share their understandings with one another.  Let them know that this is important for them to grasp, but {\it do not} simply provide ready-made answers for them!

%INDEX% Encoder versus decoder versus mux versus demux
%INDEX% Decoder versus encoder versus mux versus demux
%INDEX% Multiplexer versus demultiplexer versus encoder versus decoder
%INDEX% Demultiplexer versus multiplexer versus encoder versus decoder

%(END_NOTES)


