
%(BEGIN_QUESTION)
% Copyright 2005, Tony R. Kuphaldt, released under the Creative Commons Attribution License (v 1.0)
% This means you may do almost anything with this work of mine, so long as you give me proper credit

\noindent
Answer the following electrical safety questions:

\medskip
\item{$\bullet$} What can electric current do to your motor muscles (fingers, arms, legs) if enough of it passes through your body?
\vskip 15pt
\item{$\bullet$} What can electric current do to your heart and lung muscles if enough of it passes through your body?
\vskip 15pt
\item{$\bullet$} What special kind of hand tools are best for working on live power circuits?
\vskip 15pt
\item{$\bullet$} What type of specific medical attention may be needed for a victim of electric shock?
\medskip

\underbar{file 03343}
%(END_QUESTION)





%(BEGIN_ANSWER)

\medskip
\item{$\bullet$} What can electric current do to your motor muscles (fingers, arms, legs) if enough of it passes through your body?  {\it It may cause those muscles to involuntarily contract, placing you in danger of sustained electric shock.}
\vskip 10pt
\item{$\bullet$} What can electric current do to your heart and lung muscles if enough of it passes through your body?  {\it It may paralyze those muscles, resulting in death.}
\vskip 10pt
\item{$\bullet$} What special kind of hand tools are best for working on live power circuits?  {\it Tools with electrically-insulated handles.}
\vskip 10pt
\item{$\bullet$} What type of specific medical attention may be needed for a victim of electric shock?  {\it CPR, to revive a stopped or fibrillating heart.}
\medskip

%(END_ANSWER)





%(BEGIN_NOTES)

{\bf This question is intended for exams only and not worksheets!}.

%(END_NOTES)


