\centerline{\bf Verification of competency for ELTR courses} \bigskip 
 
The purpose of these performance assessment activities is to verify the competence of a prospective transfer student with prior work experience and/or formal education in electronics, but where the depth and rigor of the prior learning is unknown.  New students with no prior work experience or formal education in electronics must take all ELTR courses and are not allowed to challenge any by completing these activities.

\vskip 10pt

All activities are performance-based.  That is, the individual must perform all necessary predictions (calculations) based on conditions and component values specified by the instructor, then must actually {\it build} the circuit and use properly test equipment to verify those predictions.  Each assessment is pass/fail.  Either the individual is able to successfully predict, build, and test the circuit, or the individual is not able to predict, build, and/or test the circuit.

\vskip 10pt

Prospective transfer students are allowed to review the verification activities prior to performing them, but will receive no help from the instructor.  They are to study and prepare on their own.  Electronic components and test equipment for the activities will be provided by the instructor.  No books are allowed during the verification activity, but one page of notes may be used (per activity).

\vskip 10pt

``Given conditions'' for each activity will be randomly provided by the instructor at the time of verification, not prior.  This way, prospective transfer students must prove mastery of the analysis techniques by successfully working through a set of given conditions they have not seen before.

\vskip 10pt

\noindent
{\bf Competence verification activities}

\vskip 5pt

%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR100 -- DC 1}

\hskip 10pt Performance assessment: {\it Series-parallel resistor circuit (Question 1)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR105 -- DC 2}

\hskip 10pt Performance assessment: {\it RC time constant circuit (Question 2)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR110 -- AC 1}

\hskip 10pt Performance assessment: {\it Passive RC filter circuit with specified cutoff (Question 3)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR115 -- AC 2}

\hskip 10pt Performance assessment: {\it Auto-transformer (Question 4)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR120 -- Semiconductors 1}

\hskip 10pt Performance assessment: {\it AC-DC power supply (Question 5)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR125 -- Semiconductors 2}

\hskip 10pt Performance assessment: {\it BJT amplifier with specified gain (Question 6)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR130 -- Opamps 1}

\hskip 10pt Performance assessment: {\it Op-amp amplifier with specified gain (Question 7)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR135 -- Opamps 2}

\hskip 10pt Performance assessment: {\it Active RC filter circuit with specified cutoff (Question 8)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR140 -- Digital 1}

\hskip 10pt Performance assessment: {\it Logic circuit from truth table (Question 9)}
 
\vskip 10pt
%%%%%%%%%%%%%%%
\hrule \vskip 5pt
\noindent
\underbar{ELTR145 -- Digital 2}

\hskip 10pt Performance assessment: {\it Flip-flop counter circuit (Question 10)}
 
\vskip 10pt





\vfil \eject

